Ten Simple Rules for Teaching Programming

### 2017-07-21 paper.tex
Adjusted according to Barbara's comments.

\item The instructor then gives learners a multiple choice question
  that probes for misconceptions rather than simple factual recall.
  A programming example is given in Figure~\ref{fig:mcq}
  which relates to integer comparison and loops.
  There is no point asking a trivial question that all students will get right.
  The ideal questions are those where students are most likely to vote equally for each of the options.

@@

@@

For example,
a growing number of educators are including Parsons Problems
in their pedagogic repertoire~\cite{parsons,morrison-parsons}.
Rather than writing programs from scratch,
learners are given the lines of code they need to solve a problem,
but in jumbled order.
Re-ordering them to solve the problem correctly
allows them to concentrate on mastering control flow
without having to devote mental energy to recalling syntax
or the specifics of library functions.

@@

>>>>

\item The instructor then gives learners a multiple choice question
  that probes for misconceptions rather than simple factual recall.
  A programming example is given in Figure~\ref{fig:mcq}
  which relates to integer comparison and loops.
  There is no point asking a trivial question that all students will get right or one with wrong answers which no student will pick.
  The ideal questions are those where 40--60\% of students are likely to get the right answer first time, and where every wrong answer corresponds to a misconception and will be picked by at least some students~\cite[p23]{nrc-reaching}.

@@

It is also useful for motivation to make sure that students can accomplish a visible result
quickly.  Providing pre-written software libraries or source code can help to start students
closer to a meaningful result.  The idea that students must write all the code they need
themselves is the relic of a bygone era of home microcomputers (and it was not true even then).
Pick the task that you actually want to the students to engage in, and provide everything else.

@@

For example,
a growing number of educators are including Parsons Problems
in their pedagogic repertoire~\cite{parsons,morrison-parsons}.
Rather than writing programs from scratch,
learners are given the lines of code they need to solve a problem,
but in jumbled order.
Re-ordering them to solve the problem correctly
allows them to concentrate on mastering control flow
without having to devote mental energy to recalling syntax
or the specifics of library functions.  They are also liked by learners; Ericson et al.~\cite{ericson-ebook} found
that learners were more likely to attempt Parsons Problems than nearby multiple choice questions.

@@

\section*{Acknowledgments}

We are grateful to Barbara Ericson for her comments on a draft of this article.
